%!TEX root = thesis.tex
%% %% ***************** Research materials and methods *****************

%% ************************************************ 3 ************************************************

\section{Research material and methods}\label{sec:research-material-and-methods}
%\section{Tutkimusaineisto ja -menetelmät}

%% TODO: make sure below points are mentioned SOMEWHERE
\begin{verbatim}
  * Counting anomaly "probability" for individual log rows
  * Random delay! Solving issue by grouping
  * Hybrid ML with anomaly detection and regression
  => Can this give any results for forecasting?
  ?? Assumption to lean on:
    !! Ticket causing log rows are ANOMALIES in log data.
    TODO: explain why this assumption is necessary!!!
    - Log amount is not necessarily proportional to ticket creating error amount, even with info-types filtered out
    - Considerable amount of rows may be related to one, or several different, tickets
\end{verbatim}

In the next section
we explain in more detail
what the data used in the study
consists of
and what methods were used
in attempt to answer the research goals.

The data in the research is mainly made up of two parts.
The most important part is, obviously,
the log data produced by the numerous RPA processes.
The second part complementing the study
is the support ticket data written by clerks of customer banks.
In order to use the data safely in the cloud environment
it was necessary to sanitize the data
from any sensitive information.
This was done by anonymizing the log data
and using only timestamps from the support tickets.

%% TODO: explain that we are walking through the process below and each part has their own section further.
After confirming the results of anonymization,
the data was preprocessed into a better form
to make it more usable by algorithms.
More processing was done inside the pipeline
as ML Studio offered several usable components for this
but main cleaning was easier and to execute in local environment.
This was also done with Powershell scripting.

ML pipeline was created in Azure ML Studio
and several ML algorithms were compared
in order to find the most feasible for our goal in mind.
ML training was organized in two different phases
in order to find the relation between
log anomalies and technical tickets.

Finally,
the results of the trained algorithms
were validated against newly acquired production data
in order to estimate how well the initial goals of the study
were fulfilled.
These results are presented in the next section \ref{sec:results}.

%% ************************************************************************************************************

\subsection{Support ticket data}\label{subsec:meth-efecte-ticket-data}

Like all other software,
RPA components fail from time to time.
As described before,
RPA logs are verbose
making possible error identification from among it hard.
Due to that,
it is not feasible to create log parsers
that would be able to identify critical errors
from within thousands of lines of log.
When critical error happens
causing the RPA process to fail,
the banking clerks need to finish manually
the job left by the RPA robot.
Every time this happens,
these clerks then send a support request ticket
to Samlink technical help desk
and ask to fix the issue.

When clerks send the ticket to technical support
a verbose description of the situation is written
to help developers to identify the problem.
This description often contains sensitive end customer information
like bank account details and social security numbers.
To avoid privacy issues when processing this data,
it was decided to use only timestamps of the tickets.
The resulting data was practically a list of date and time values.
More about the issue from privacy point of view
is described in section~\ref{subsec:meth-data-anonymization}.

%% ************************************************************************************************************

\subsection{RPA log data}\label{subsec:meth-rpa-log-data}
Robotic process algorithms used in Samlink
are designed to ease the workload of bank clerks.
RPA robots work mostly with loan applications
among other routine tasks
that require mostly manual labor.
\todo{Check!}

Like other software,
RPA also produces log data during runtime.
As several RPA robots are running
the amount of log produced daily is also significant.
\todo{How many RPA:s? How many customers? How much log data?}
%% TODO: How many RPAs
%% TODO: how many customers are they dealing with?
%% TODO: AMOUNTS!
This log data is not in consistent structure
being formed out of typical CSV data
injected with even more inconsistent JSON data
that varies in contents vastly.
\todo{refer to appendices, include examples of data}

RPA log data is stored in SQL database.
The database is split in live production log
that is gathered for few months
and then moved to archive that has
several years worth of log.
\todo{check live timescale}
%% TODO: Check

In this study we used archived data
as it was easier to acquire in one run
without the need to merge different parts together.
Archive also had
data that was considered as sufficient amount
for machine learning algorithm training.
\todo{how much really?}

\begin{itcomment}
    Next up we'll explain some key features about the log data
    such as timestamps, robot names, messages etc.

    The important part to keep in mind here is that message is in two forms:
    message and rawmessage.
    Without rawmessage, the data was in pure CSV-format.
    However, it was not certain that rawmessage would not hold usable data for ML~.
    In the end, the usage of rawmessage was mostly skipped
    as it demanded too much resources in ML Studio to process.
    In the data preprocessing phase the rawmessage was kept along
    and it lead to some interesting and most likely reusable preprocessing scripts.
\end{itcomment}

%% ************************************************************************************************************

\subsection{Data anonymization}\label{subsec:meth-data-anonymization}

\subsubsection*{Support ticket data privacy}
Samlink handles highly sensitive banking customer data in its processes,
such as personal identification numbers, home addresses, email addresses and bank account numbers.
All possibly sensitive data had to be removed
before data could be transferred out from production environment to cloud.
Due to bureaucratic reasons,
technical support tickets were under more strict policies.
Because of this,
they were allowed to be used in the research
on condition that no business critical nor customer sensitive information
was processed in the first place.
Only way to assure this
was to select solely timestamp fields from ticket data.
Thus, no sanitation for ticket data was needed
as ticket data consisted of only list of datetime values.

\subsubsection*{RPA log data sanitization}
Information privacy is one of the key values in Samlink business promise
as company develops high security banking applications
and processes sensitive customer data.
Thus, several aspects were needed to take into consideration
before log data could be authorized for thesis study usage.
To improve privacy,
it was decided to assume
that personal customer details are not critical information
for ML algorithm training
if goal is to find possible problems in RPA runtime
and not detect individual customer related problems.
This way it was not necessary to achieve adequate security
by less secure and more effort consuming ways
such as pseudonymization or k-anonymization,
which would have also required strict inspections
before data could have been approved for cloud processing.
\todo{References?}
%% TODO: references?
%% TODO: Refer to k-anonymization and pseudonymization. Explain BRIEFLY
\begin{itcomment}
    Here we could explain more about pseudonymization and k-anonymization,
    but is it necessary as they were not used or considered?
    It would bring something more to the study, of course,
    but is it worth the time?
\end{itcomment}

As production environment is built on Microsoft Server based solution,
and because it was highly unrecommended
to install additional software to the production server,
data acquiring and anonymization tools were chosen
based on what was already usable in the RPA production environment.
Microsoft Powershell offers sufficient tools
for database SQL querying
and stream editing.
The amount of data was significant
which made straight file editing impossible
due to the memory limitations.
Thus, stream editing was necessary
for finding and replacing
sensitive information from the data.
\todo{maybe references?}
%% TODO: References!

Anonymization took good proportion of the time in workdays
as processes were slow,
the amount of data was huge
and multiple re-runs were needed
before the results were seemed adequate.
\todo{Appendix of the script used. Does this need more explaining?}
%% TODO: appendix of the script used

%% ************************************************************************************************************

\subsection{Data formatting}\label{subsubsec:data-formatting}
At the beginning of the research,
the log data from RPA was in SQL database.
However,
the database used was not "pure"
in a way that typical relational databases are,
but some columns included JSON-formatted data in them.
For ML algorithms to be able to read the given data with ease
this kind of impurities needed to be cleared from the data.

When feeding the log data to anomaly detection algorithm
it was necessary that all the rows were
as minimally unique as possible
in order to use the pattern finding abilities of the algorithm.
Too unique data points would have made all of them anomalies
compared to each other.
Thus, all unique features were stripped from the data,
such as the fingerprint value
that was unique for each data point.
\begin{itcomment}
    Also,
    job ID information and timestamps of the rows
    were removed momentarily from within the rawmessage.
\end{itcomment}

\begin{itcomment}
    Some interesting formatting solutions were used in this phase.
    Rawmessage was practically created again
    so that it fitted in the CSV format.
    This should be explained in some level of detail.
\end{itcomment}

\todo{check above section so it makes sense}
%% TODO: this was done with case:RawMessage
%% TODO: fix above to make sense


%% ************************************************************************************************************

\subsection{Azure environment}\label{subsec:meth-azure-environment}

\todo{This section is under construction! Here are some things we are discussing here:}
\begin{itcomment}
    Azure resources, such as virtual networks, storage spaces, connections to ML studio \etc

    More info about ML studio,
    computing clusters, jobs, datasets and such.
    What kind of resources were usable based on the issue at hand
    and limitations by the company (cost, basically).
    We discuss some things about Azure ML Studio
    but only in extent of what parts needed configuring.
    More general info about ML Studio should be in chapter 2.
\end{itcomment}

%% TODO: <Azure resources, virtual network etc.>
% Several different ML methods are usable with Azure ML Studio.
% %%TODO: open up
%% TODO: Azure architecture


%% ************************************************************************************************************


\subsection{Machine learning pipeline}\label{subsec:meth-ml-pipeline}

\todo{this section is under construction}
As stated in section~\ref{subsec:bg-ml-field},
the approach in this thesis is,
if expression is allowed, unorthodox.
Typically,
it is not a good idea to use
same data points in ML algorithm training and validating.
Acting otherwise
leads to algorithm processing with
same data it was trained with
thus creating a situation
where algorithm already knows what to do with the current datapoint.
If the results were validated after this
the algorithm would get unreliable score
as it had the validation data already in the training phase.
This could be compared to
giving some right answers to students
during test and scoring test results as if
no help was given.

\todo{explain why we did it anyway!}

\begin{itcomment}
    Depending on the results (still working on it...)
    it is possible that this unorthodox training method didn't bring much results
    compared to proper training pipeline.
\end{itcomment}

Initial plan when starting the ML pipeline testing
was to feed the log data to anomaly detection algorithm
and try to get some sort of estimate of possible anomaly count.
This plan had several problems.

First, as stated, logging is very abundant
and several thousands of rows is logged
during a single day.
Some errors encountered are not critical
and RPA robot is able to recover from them
finalizing the initial task.
This means, that errors that could be deemed anomalous
may not result to a ticket in the end.

In addition,
one single error case
may be linked to several problems in runtime,
meaning that one ticket received is,
in fact, linked to multiple, dozens or
even hundreds of log rows.

Two different algorithms were needed.
In phase 1,
algorithm defines how likely one datapoint
is to be considered an anomaly.
In phase 2,
another algorithm aims to predict
how many tickets are to be expected to receive
within a time frame.

\todo{Under construction below:}

%% TODO: Mention that data splits in phase 1 have to be un-random
%% Otherwise, possible anomaly values used in phase 2 would be randomly included
%% Data in phase 1 need to be chronological!


%% TODO: Results: Feature Hashing runs out of memory in Model Training with full data (unconventional training)
%% Trying with smaller splits, which, once again, reduces data amount.

\begin{itcomment}
    Next in this subsection, ML studio pipeline used is explained in more detail.
    This means pictures about the pipeline,
    explanations about the components used and their parameters,
    etc. etc.

    Some of the content might be wise to move to the Results section.
    This needs more somewhat more thinking, also based on the results...
\end{itcomment}

%% TODO: unorganized text below!

%% TODO: Next up is outdated
%
%Usually <with usual ml methods> the estimates
%created using ML algorithms
%are formed based on the certain features
%presented on a one element of the data,
%or on one row.
%This means that in typical case,
%there is one column in the data
%given to the ML algorithm
%that is removed from the training data
%and this column value is what algorithm
%aims to predict.
%
%In this study case, however,
%data does not contain clear values
%that are being estimated
%and that can be used as comparison.
%
%\begin{tabular}{cccc}
%    LOG\_DATA \\
%    a=date & b=msg & c=\etc & \\
%    a & b & c & n1 \\
%    a & b & c & n2 \\
%    a & b & c & n3 \\
%    a & b & c & n4
%\end{tabular}
%
%\begin{tabular}{c}
%    EFECTE\_DATA \\
%    A YYYY.MM.DD hh:mm:ss \\
%    B YYYY.MM.DD hh:mm:ss \\
%    C YYYY.MM.DD hh:mm:ss \\
%    D YYYY.MM.DD hh:mm:ss \\
%    E YYYY.MM.DD hh:mm:ss
%\end{tabular}
%\\
%n1 = SUM(AB) \\
%n2 = SUM(C) \\
%n3 = SUM(DE) \\
%=> \\
%We could try to predict nx
%but usually this is done
%by making estimate based on
%a, b and c.
%Instead,
%we aim to estimate the sum of events
%in timeframe.
%We should also skip event instances
%that are close to each other
%to avoid counting multiple values
%linked to same error
%as different possible ticket creators.


\subsubsection*{Memory issues and limitations}
Memory is crucial in ML training
as multiple steps happen
and data is formatted \etc. %% TODO: fix!
While building ML pipeline in Azure ML studio,
a memory issue emerged
that affected several components
and caused serious limitations
in terms of usable components and data size.
Due to the time limits of this study
this issue was not resolved
and the problem behind it was not found.
As several conditions
considering the environment costs
were already issued by the company,
the issue was declared to be linked with
compute instance property limitations.
However, this was not certain.

%% TODO: limitations to components
%% limitations to data size
%% effects on choises in components?


\subsubsection*{Feature format for PCA-ADA}
%% TODO: n-gram vs pure data input
In Azure ML Studio
there is only one module selectable
for anomaly detecting,
the PCA-based anomaly detection module,
which is explained in section~\ref{subsec:bg-pca-ada}.
However,
with textual input like logs
it can be used at least in two ways.
First,
input data can be fed to
the algorithm trainer as is,
letting the PCA-based ADA component %% TODO: Explain ADA
do the work without further modifying the log rows.
This way,
the component tries to recognize the anomalies
based on all the information included in the row.
Practically this means
that the component processes data in textual format
making each row in the input
a feature as a whole
to consider.
\todo{PCA-ADA should be explained in background-section}

Second option is to
convert the textual features
into numerical n-gram features.
Each word or n-gram
is now a number of said instances found on
the row being processed,
and each row can be presented
as a sequence of numbers
indicating the number of those features.

%% TODO N-gram theory should be explained and referred properly. Here or in background!
N-grams can in addition have a weight
based on the frequency they appear
in the entire data.
Different weights usable in Azure ML component
are listed below.

\begin{enumerate}
    \item Binary Weight
    \item TF Weight
    \item IDF Weight
    \item TF-IDF Weight
\end{enumerate}

\todo{Explain different weights and open up more Azure ML Studio PCA-component}

%% TODO: RESULTS:
%   Pure n-gram feature component using skipped
%   Only 2% of the data could be used. Not enough.
%


\subsubsection*{Anomaly probability}
%% TODO: PCA output
\begin{itcomment}
    Here we explain what PCA-component outputs and how the result is used in the pipeline.
\end{itcomment}

\subsubsection*{Statistical features}
%% TODO: combination with ticket data. SQL queries
\begin{itcomment}
    This part explains some statistical features used when starting regression training
    in hybrid ML phase 2.
    These features consist of both log row amounts
    and PCA-component output values.
    All these values are grouped together in timescales.
\end{itcomment}


\subsubsection*{Regression based estimating}
%% TODO: parameters?
%% Ticket amount forecasting
\begin{itcomment}
    Here is more information about different regression algorithms
    used in ML pipeline.
    Some basic information about all of them is given so the results are understandable
    by reader in the Result section.
\end{itcomment}

\begin{enumerate}
    \item Linear regression
    \item Decision forest regression
    \item \etc
    \item \etc
\end{enumerate}


\clearpage